---
title: "Power Analysis: Adaptive N-of-1 Simulation"
author: "Martin Braquet, Riki Dewan"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: cosmo
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,    # Show code for reproducibility
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 8,
  fig.height = 5,
  dpi        = 300,
  cache      = TRUE     # Crucial: caches the long Bayesian simulations
)

library(tidyverse)
library(brms)
library(furrr)
library(cmdstanr)
library(scales)
library(here)

# Load project-specific utility functions
source(here("analysis", "utils", "model.R"))
source(here("analysis", "utils", "sim.R"))
source(here("analysis", "utils", "plotting.R"))
source(here("analysis", "utils", "power.R"))

# Parallel processing setup for brms/cmdstanr
options(mc.cores = parallel::detectCores())
set.seed(42)
```

## Overview

This document reports the simulation-based power analysis for the **Maya Care and Grow** N-of-1 crossover trial. We utilize a Bayesian adaptive framework to determine the probability of resolving treatment superiority (or equivalence) for individual children within a clinical window of 36 sessions.

### Trial Design Parameters

-   **Design**: Randomized blocked crossover (Block size = 4).
-   **Population**: $N = 25$ children.
-   **Outcome**: BRES-10 Engagement Scale.
-   **Model**: Bayesian Hierarchical Linear Model.

------------------------------------------------------------------------

## 1. Simulation Configuration

We define the expected effect sizes and the adaptive parameters. The "Resolution" of a child's profile is checked every 4 sessions after an initial 12-session burn-in.

```{r params}
CONFIG <- list(
  effect_size  = 2.0,
  n_children   = 25,
  n_sims       = 28,      # Number of iterations per profile
  max_sessions = 36,
  check_every  = 4,
  min_sessions = 12
)

print(glimpse(CONFIG))
```

------------------------------------------------------------------------

## 2. Adaptive Simulation Sweep

The following block executes the Monte Carlo simulation. We iterate through four potential child profiles: *Strong Winner*, *Weak Winner*, *Multiple Winners*, and *No Differential*.

```{r run-simulation, cache=TRUE}
# This chunk is cached because Bayesian fitting is computationally expensive
adaptive_results <- run_adaptive_sweep(
  n_sims          = CONFIG$n_sims,
  effect_size     = CONFIG$effect_size,
  n_children      = CONFIG$n_children,
  min_sessions    = CONFIG$min_sessions,
  max_sessions    = CONFIG$max_sessions,
  check_every     = CONFIG$check_every
)
```

------------------------------------------------------------------------

## 3. Results: Resolution Curves

The resolution curve represents the cumulative probability that the Bayesian stopping rules (Superiority, AIPE, or ROPE) are met before the session cap.

```{r plot-results, echo=FALSE}
plot_resolution_curve(
  adaptive_results, 
  max_s = CONFIG$max_sessions, 
  check_every = CONFIG$check_every
)
```

**Interpretation:** Based on the simulation, a cap of **28 sessions** provides a robust balance between statistical power (approx. 83% overall resolution) and clinical feasibility (7 weeks of intervention).

------------------------------------------------------------------------

## Session Information

For reproducibility purposes, the versions of all packages used in this analysis are listed below.

```{r session-info}
sessionInfo()
```
