---
title: "Prior Sensitivity Analysis"
author: "Martin Braquet, Riki Dewan"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 9,
  fig.height = 6,
  dpi        = 300,
  cache      = TRUE
)

library(tidyverse)
library(brms)
library(here)

# Load specialized utility functions
source(here("analysis", "utils", "model.R"))
source(here("analysis", "utils", "sim.R"))
source(here("analysis", "utils", "plotting.R"))
source(here("analysis", "utils", "power.R"))
source(here("analysis", "utils", "stop_criteria.R"))
source(here("analysis", "utils", "sensitivity.R"))

set.seed(42)
```

## Purpose

A critical step in Bayesian N-of-1 trials is assessing how the choice of prior distributions influences the posterior estimates and the resulting clinical decisions (stopping rules). This analysis compares our **Target Priors** against **Non-Informative (Flat) Priors** and **Highly Regularizing Priors**.

## 1. Parameters & Prior Specifications

We test the sensitivity across a cohort of 25 children, simulating up to 48 sessions to observe the long-term convergence behavior of the different prior structures.

```{r config}
SENS_CONFIG <- list(
  n_sims       = 28,
  effect_size  = 2.0,
  n_children   = 25,
  max_sessions = 48
)
```

## 2. Sensitivity Sweep

The following execution compares the probability of resolving treatment superiority under varying prior "strength."

```{r run-sensitivity, cache=TRUE}
# This process is computationally intensive as it fits multiple models per simulation
sensitivity_results <- run_prior_sensitivity(
  n_sims       = SENS_CONFIG$n_sims,
  effect_size  = SENS_CONFIG$effect_size,
  n_children   = SENS_CONFIG$n_children,
  max_sessions = SENS_CONFIG$max_sessions
)
```

------------------------------------------------------------------------

## 3. Visualization of Influence

We look for the "Stability" of the resolution. If the prep recommendations from informative and non-informative priors are similar, it suggests the data (BRES-10 scores) is strong enough to overwhelm the prior.

```{r plot-sensitivity}
sensitivity_results
```

**Interpretation:** The overall average agreement is above 85% and the delay in prep resolution is less than 4 sessions across prior specifications, suggesting that the clinical stopping decisions are driven by observed participant behavior rather than prior assumptions.

------------------------------------------------------------------------

## Session Metadata

```{r session-info}
sessionInfo()
```
