---
title: "Covariate Sensitivity Analysis"
author: "Martin Braquet, Riki Dewan"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: lumen
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 9,
  fig.height = 6,
  dpi        = 300,
  cache      = TRUE
)

library(tidyverse)
library(brms)
library(here)

# Load specialized utility functions
source(here("analysis", "utils", "model.R"))
source(here("analysis", "utils", "sim.R"))
source(here("analysis", "utils", "plotting.R"))
source(here("analysis", "utils", "power.R"))
source(here("analysis", "utils", "stop_criteria.R"))
source(here("analysis", "utils", "sensitivity.R"))

set.seed(42)
```

## Purpose

In a real-world clinical setting like **Maya Care and Grow**, engagement scores may be influenced by environmental factors unrelated to the preparation activity. This sensitivity analysis assesses the model's ability to isolate the **treatment effect** from common covariates, specifically:

-   **Assistant/Practitioner Effects**: Variance introduced by different staff members.

-   **Age**: There is wide variation in engagement depending on the child's age.

## 1. Simulation Parameters

We simulate a scenario where these covariates have a known influence on the BRES-10 engagement score to verify if our Bayesian hierarchical model correctly partitions the variance.

```{r config}
COV_CONFIG <- list(
  n_sims       = 100,
  effect_size  = 2.0,      # True treatment effect
  n_children   = 25,
  n_sessions   = 36
)

print(COV_CONFIG)
```

## 2. Covariate Sensitivity Sweep

We run the simulation comparing a "Base Model" (treatment only) against Covariate-Adjusted Models. This allows us to quantify the "Precision Gain" when external noise is accounted for.

```{r run-covariate-analysis, cache=TRUE}
# This function fits models with and without nuisance parameters
combined_results <- covariate_sensitivity(
  effect_size = COV_CONFIG$effect_size,
  n_sessions  = COV_CONFIG$n_sessions,
  n_children  = COV_CONFIG$n_children,
  n_sims      = COV_CONFIG$n_sims
)
```

------------------------------------------------------------------------

## 3. Comparative Results

From the output above, there is 100% alignment in prep recommendation for each child.

**Interpretation:** The inclusion of fixed-effect covariates reduced the prep variance without change in recommendation, resulting in more rapid convergence of individual treatment effects without introducing bias.

------------------------------------------------------------------------

## Session Info

```{r session-info}
sessionInfo()
```
