---
title: "Main Analysis"
author: "Martin Braquet, Riki Dewan"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: lumen
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 9,
  fig.height = 6,
  dpi        = 300,
  cache      = TRUE
)

library(tidyverse)
library(brms)
library(here)

# Load specialized utility functions
source(here("analysis", "utils", "model.R"))
source(here("analysis", "utils", "sim.R"))
source(here("analysis", "utils", "plotting.R"))
source(here("analysis", "utils", "power.R"))
source(here("analysis", "utils", "stop_criteria.R"))
source(here("analysis", "utils", "sensitivity.R"))

set.seed(42)
```

## Purpose

The main analysis checks the stopping conditions with the current data and assigns the recommended preparation to the resolved children.

Descriptive analysis of child ratings per prep:
```{r}
boxplot_per_child()

file_path <- here("data", "sessions.csv")
data <- read_csv(file_path)
glimpse(data)

mean_by_prep_child <- data %>%
  group_by(child_id, prep) %>%
  summarise(
    mean_rating = mean(engagement, na.rm = TRUE),
    n_sessions  = n(),
    .groups = "drop"
  ) %>%
  arrange(child_id, prep) %>%
  mutate(mean_rating = round(mean_rating, 2))

save_csv(mean_by_prep_child, name = "ratings_per_child_and_prep")

sessions_per_child <- data %>%
  group_by(child_id) %>%
  summarise(
    mean_rating = mean(engagement, na.rm = TRUE),
    n_sessions  = n(),
    .groups = "drop"
  ) %>%
  arrange(child_id) %>%
  mutate(mean_rating = round(mean_rating, 2))

write.csv(sessions_per_child, here::here("results", "sessions_per_child.csv"), row.names = FALSE)

chains <- 4
fit <- fit_model_fresh(
  data,
  threads = threading(chains),
  chains = chains,
  iter = 2000
)

summary_table <- posterior_summary(fit) %>%
  as.data.frame() %>%
  rownames_to_column(var = "parameter")
save_csv(summary_table, name = "fit_summary")

write.csv(as_draws_df(fit), here::here("results", "draws.csv"), row.names = FALSE)

results <- check_stopping_per_child(fit)
print(results, n=100)
save_csv(results, name = "stopping_checks")
```

## Posterior predictive checks

The convergence diagnostics in `fit_model_fresh()` (R-hat, ESS, divergences) only confirm the sampler explored the posterior reliably; they say nothing about whether the model *fits* the data. Engagement is a bounded mean of BRES-10 ratings modelled with a Gaussian likelihood, so we check whether data simulated from the fitted model reproduce the observed range, spread, and per-child means. Systematic mismatches (e.g. predicted values outside the valid range, or under-dispersion) would flag misspecification of the likelihood.

```{r ppc}
plot_ppc(fit)
```
