---
title: "Main Analysis"
author: "Martin Braquet, Riki Dewan"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    theme: lumen
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo       = TRUE,
  warning    = FALSE,
  message    = FALSE,
  fig.width  = 9,
  fig.height = 6,
  dpi        = 300,
  cache      = TRUE
)

library(tidyverse)
library(brms)
library(here)

# Load specialized utility functions
source(here("analysis", "utils", "model.R"))
source(here("analysis", "utils", "sim.R"))
source(here("analysis", "utils", "plotting.R"))
source(here("analysis", "utils", "power.R"))
source(here("analysis", "utils", "stop_criteria.R"))
source(here("analysis", "utils", "sensitivity.R"))

set.seed(42)
```

## Purpose

The main analysis checks the stopping conditions with the current data and assigns the recommended preparation to the resolved children.

## Steps

1. Load latest data (etl.R)
2. Check observation box plots (in results/observation_plots)
3. Run analysis (main.R)
4. Check stopping conditions (results/stopping_checks.csv)
5. Check posterior forest plots (in results/posterior_plots)
6. Assign recommended preparations

```{r}
source("analysis/utils/etl.R")
source("analysis/utils/main.R")
```

Descriptive analysis of child ratings per prep:
```{r}
boxplot_per_child()
```

## Posterior predictive checks

The convergence diagnostics in `fit_model_fresh()` (R-hat, ESS, divergences) only confirm the sampler explored the posterior reliably; they say nothing about whether the model *fits* the data. Engagement is a bounded mean of BRES-10 ratings modelled with a Gaussian likelihood, so we check whether data simulated from the fitted model reproduce the observed range, spread, and per-child means. Systematic mismatches (e.g. predicted values outside the valid range, or under-dispersion) would flag misspecification of the likelihood.

```{r ppc}
plot_ppc(fit)
```
